Arbeidskrav våren 2022

### 2022-01-13 MSB106_Arbeidskrav_V22_Backup.Rmd
Endret navn på variabel

```{r Bosted_Sunnhordland_1}
sun_bos %>% 
  ggplot(mapping = aes(x = År, y = `Alle Næringer`)) +
  geom_line() +
  labs(title = "Sunnhordaland", x = "År", y = "Antall ansatte i  \n alle næringer") +
  theme(axis.title.y = element_text(angle=0))+ 
  scale_x_continuous(breaks = seq(2008, 2020, by = 1))
```

>>>>

```{r Bosted_Sunnhordland_1}
sun_bos %>% 
  ggplot(mapping = aes(x = År, y = Totalt)) +
  geom_line() +
  labs(title = "Sunnhordaland", x = "År", y = "Antall ansatte i  \n alle næringer") +
  theme(axis.title.y = element_text(angle=0))+ 
  scale_x_continuous(breaks = seq(2008, 2020, by = 1))
```
